\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{Physics Engine Development Log}
\author{Emil Motrøen}
\date{Project Start: December 21st, 2024}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{Introduction}
This document serves as a development log for the project. It includes notes on progress, decisions made, and any issues encountered.

\section{Project Setup}
\subsection{Initial Setup}
\begin{itemize}
    \item Created project repository.
    \item Set up initial directory structure.
    \item Added basic CMake configuration.
\end{itemize}

\subsection{Tool Installation}
\begin{itemize}
    \item Installed necessary tools: \texttt{cmake}, \texttt{g++}, \texttt{clang}, \texttt{glad}, \texttt{glfw}, \texttt{doxygen}.
    \item Verified installations and versions.
\end{itemize}

\section{Development Log}
\subsection{2024-12-21}
\begin{itemize}
	\item Created basic project files, directories and basic files setup.
	\item Added support for using either g++ or Clang when compiling.
	\item Added additional compiler flags and a file for pre-compiled headers.
	\item Implemented basic triangle on the screen using OpenGL.
	\item Fixed an issue where g++ and Clang have a few different compiler flags by removing the non-shared ones.
	\item Added a bash script for building and running the code, build\_and\_run.sh.
\end{itemize}

\subsection{2024-12-22}
\begin{itemize}
	\item The build\_and\_run.sh script now can produce verbose output.
	\item The build\_and\_run.sh script converts input to lowercase to make comparisons easier.
	\item Added a bash script to run Doxygen to create documentation easier, gen\_docs.sh.
	
\end{itemize}

\subsection{2024-12-23}
\begin{itemize}
    \item Implemented basic build script.
    \item Added error handling to the build script.
    \item Integrated Doxygen for documentation generation.
\end{itemize}

\subsection{2024-12-24}
\begin{itemize}
    \item Updated CMakeLists.txt to include custom targets.
    \item Fixed issues with cache loading in CMake.
    \item Started writing \LaTeX{} document for development log. Earlier entries in this section are based on the git messages created before this document.
\end{itemize}

\subsection{2024-12-29}
\begin{itemize}
	\item Made a commit of the new devlog after a Christmas break. 
\end{itemize}

\section{Issues and Resolutions}
\subsection{Issue: Cache Loading Error}
\begin{itemize}
    \item \textbf{Description:} Encountered "could not load cache" error when adding custom target in CMake.
    \item \textbf{Resolution:} Ensured proper order of commands in CMakeLists.txt and verified script paths.
\end{itemize}

\subsection{Issue: Compiler Flags Compatibility}
\begin{itemize}
    \item \textbf{Description:} Some compiler flags were not compatible with both \texttt{g++} and \texttt{clang}.
    \item \textbf{Resolution:} Remove all compiler flags that were not compatible with both compilers.
\end{itemize}

\section{Future Work}
\begin{itemize}
    \item Continue updating the development log with daily progress.
    \item Finish the OpenGL stuff relatively quickly so that work on the actual physics engine can start.
\end{itemize}

\end{document}